Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2020-05-27 Manuscript/manuscriptPGPE.tex
Update ECC-lipid data

      \hline
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}   &0          & 0  & 350:88 & 26265 & 0  &  298  & 400 & 350 & \cite{Lipid17POPCPOPG8020} \\
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0.1& 350:88 & 26124 & 47 &  298  & 400 & 150 & \cite{Lipid17POPCPOPG8020100mMCaCl} \\
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 1.0& 350:88 & 24840 & 475 &  298  & 1200 & 200 & \cite{Lipid17POPCPOPG80201000mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0  & 150:150 & 31572 & 0  &  298  & 320 & 200 & \cite{Lipid17POPCPOPG5050} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}     &0          & 0.1& 150:150 & 31401 & 57 &  298  & 720 & 198 & \cite{Lipid17POPCPOPG5050100mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 1.0& 150:150 & 29865 & 569 &  298  & 720 & 200 & \cite{Lipid17POPCPOPG50501000mMCaCl} \\
      \hline
      POPC             & Berger \cite{??} \todoi{This is probable not plain berger, correct force filed should be described.}  &0  & 0  & 256 & 10240 & 0  &  300  & 300 & 200 & \cite{POPCberger300K} \\
      POPC:POPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.} &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{POPC1POPE1berger} \\
      POPC:DOPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 128 & 10240 & 0  &  300  & 300 & 200 & \cite{POPC1DOPE1berger} \\
     \hline
      DOPC             & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 256 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPCberger300K} \\
      DOPC:DOPE (1:1)  & Berger \cite{??}   \todoi{This is probable not plain berger, correct force filed should be described.}        &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPC1DOPE1berger} \\
    \end{tabular}
  \end{minipage}
  %\end{sidewaystable*}
  \todo{New CHARMM simulations are still to be ran.} \\
  \todo{Citation and ion model for GROMOS-CKP?} \\
  \todo{Citation and description for ''Berger'' model?}
\end{table*}

>>>>

      \hline
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0  & 350:88 & 26265 & 0  &  298  & 400 & 350 & \cite{Lipid17POPCPOPG8020} \\
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0.1& 350:88 & 26124 & 47 &  298  & 400 & 250 & \cite{Lipid17POPCPOPG8020100mMCaCl} \\
      POPC:POPG (4:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 1.0& 350:88 & 24840 & 475 &  298  & 1200 & 200 & \cite{Lipid17POPCPOPG80201000mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0  & 150:150 & 31572 & 0  &  298  & 320 & 200 & \cite{Lipid17POPCPOPG5050} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 0.1& 150:150 & 31401 & 57 &  298  & 720 & 198 & \cite{Lipid17POPCPOPG5050100mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17 / Dang \cite{gould18,smith94,dang06}        &0          & 1.0& 150:150 & 29865 & 569 &  298  & 720 & 200 & \cite{Lipid17POPCPOPG50501000mMCaCl} \\
      \hline
      POPC:POPG (1:1)        & Lipid17ecc / ECC-ions \cite{pluharova14,kohagen16,martinek18}     &0          & 0  & 150:150 & 31572 & 0  &  298  & 347.8 & 333 & \cite{Lipid17eccPOPCPOPG5050} \\
      POPC:POPG (1:1)        & Lipid17ecc / ECC-ions \cite{pluharova14,kohagen16,martinek18}     &0          & 0.1& 150:150 & 29865 & 54 &  298  & 400 & 300 & \cite{Lipid17eccPOPCPOPG5050100mMCaCl} \\
      POPC:POPG (1:1)        & Lipid17ecc / ECC-ions \cite{pluharova14,kohagen16,martinek18}     &0          & 1.0& 150:150 & 29865 & 569 &  298  & 720 & 200 & \cite{Lipid17eccPOPCPOPG50501000mMCaCl} \\
      \hline
      POPC             & Berger \cite{??} \todoi{This is probable not plain berger, correct force filed should be described.}  &0  & 0  & 256 & 10240 & 0  &  300  & 300 & 200 & \cite{POPCberger300K} \\
      POPC:POPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.} &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{POPC1POPE1berger} \\
      POPC:DOPE (1:1)  & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 128 & 10240 & 0  &  300  & 300 & 200 & \cite{POPC1DOPE1berger} \\
     \hline
      DOPC             & Berger \cite{??}  \todoi{This is probable not plain berger, correct force filed should be described.}         &0          & 0  & 256 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPCberger300K} \\
      DOPC:DOPE (1:1)  & Berger \cite{??}   \todoi{This is probable not plain berger, correct force filed should be described.}        &0          & 0  & 128 & 11008 & 0  &  300  & 300 & 200 & \cite{DOPC1DOPE1berger} \\
    \end{tabular}
  \end{minipage}
  %\end{sidewaystable*}
  \todo{New CHARMM simulations are still to be ran.} \\
  \todo{Citation and ion model for GROMOS-CKP?} \\
  \todo{Citation and description for ''Berger'' model?} \\
  \todo{Missing Zenodo entries of Lipid17 should be updated to the ones with corrected dihedrals.}\\
  \todo{Lipid17ecc simulations to be added.}
\end{table*}

### 2020-05-27 Manuscript/manuscriptPGPEsuppl.tex
Update results with corrected dihedral for Lipid17 POPG from https://github.com/NMRLipids/NMRlipidsIVPEandPG/issues/12
Update ECC-lipid data

@@

\noindent {\it POPG} Data is available at \cite{slipidsPOPGfiles}. \todo{Simulation details by F. Favela.}

\noindent {\it DPPG} Data in 298~K is available at \cite{slipidsDPPGfilesT298K} and in 314~K at \cite{slipidsDPPGfiles}.  \todo{Simulation details by F. Favela.}

@@

>>>>

\noindent {\it POPE with additional NaCl} \todo{Simulation details by A. Peon.
  I have assumed that ion parameters are default Slipids, i.e., {\AA}qvist, please correct if this is not true.
}

@@

\noindent {\it POPG} Data is available at \cite{slipidsPOPGfiles}. \todo{Simulation details by F. Favela.
  I have assumed that ion parameters are default Slipids, i.e., {\AA}qvist, please correct if this is not true.}

\noindent {\it POPG with additional NaCl} \todo{Simulation details by A. Peon.
  I have assumed that ion parameters are default Slipids, i.e., {\AA}qvist, please correct if this is not true.}

\noindent {\it DPPG} Data in 298~K is available at \cite{slipidsDPPGfilesT298K} and in 314~K at \cite{slipidsDPPGfiles}.
\todo{Simulation details by F. Favela.
  I have assumed that ion parameters are default Slipids, i.e., {\AA}qvist, please correct if this is not true.}

\noindent {\it POPC:POPG mixture with additional NaCl} \todo{Simulation details by A. Peon.
  I have assumed that ion parameters are default Slipids, i.e., {\AA}qvist, please correct if this is not true.}

@@

\subsection{Lipid17}

\subsection{ECC-LIPID POPG}
In ECC-lipid models, electronic continuum correction (ECC) is applied to 
implicitly include the missing electronic polarizability into the force field description \cite{melcr18,melcr19}.
In practise, this is implemented by scaling the charges and Lennard-Jones $\sigma$s of headgroup, glycerol backbone, and carbonyl regions
of Amber Lipid14/17 models are scaled by constant factors.
Here, we follow the approach that previously improved ion binding to bilayers containing negatively charged PS lipids \cite{melcr19}:
ECC-POPC parameters (scaling factors $f_q$=0.8 and $f_\sigma$=0.89 applied to Lipid14 POPC parameters) \cite{melcr18} were used for POPC
and scaling factors of $f_q$=0.75 and $f_\sigma$=0.89 were applied to the charges and Lennard-Jones $\sigma$s of headgroup, glycerol backbone, and carbonyl regions
of Amber Lipid17 POPG parameters. The Lipid17 parameters (described above) and initial configurations
were taken from Ref. \cite{POPGlipid17} with the correct dihedral type,
and the resulting parameters are available from Ref. \citenum{??}. ECC-ion parameters with the scaled charges \cite{pluharova14,kohagen16,martinek18},
downloaded from \url{bitbucket.org/hseara/ions/src/master/}, were used in these simulations.
